Scaling rates of true polar wander in convecting planets and moons

### 2017-09-13 tpw_rate.tex
Close quotes

Much of the debate about the magnitude of TPW on Earth comes down to the question of how big $\theta$ can be.
\citet{kirschvink1997evidence} hypothesized about an inertial interchange event, where $\theta$ alters by approximately 90$^\circ$,
and can lead to large ($\sim90^\circ$) TPW over time (a process which they termed ``inertial interchange TPW, or IITPW).
Conversely, many geodynamic simulations of recent TPW assume that $\theta$ is small \citep{steinberger1997changes}.
In this section we seek to characterize the maximum value for $\theta$ in terms of the dimensionless parameters.

>>>>

Much of the debate about the magnitude of TPW on Earth comes down to the question of how big $\theta$ can be.
\citet{kirschvink1997evidence} hypothesized about an inertial interchange event, where $\theta$ alters by approximately 90$^\circ$,
and can lead to large ($\sim90^\circ$) TPW over time (a process which they termed ``inertial interchange'' TPW, or IITPW).
Conversely, many geodynamic simulations of recent TPW assume that $\theta$ is small \citep{steinberger1997changes}.
In this section we seek to characterize the maximum value for $\theta$ in terms of the dimensionless parameters.
